\section*{Publications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[allowframebreaks]{Publications}
    \begin{block}{International peer-reviewed conferences with proceedings}
        \begin{enumerate}
            \item {\footnotesize\textbf{William Pensec}, Vianney Lapôtre, and Guy Gogniat. 2023. Another Break in the Wall: Harnessing Fault Injection Attacks to Penetrate Software Fortresses. In Proceedings of the First International Workshop on Security and Privacy of Sensing Systems (SensorsS\&P), 2023. \textbf{Best paper award}~\cite{PLG-23-SensorsSP}}
            \item {\footnotesize\textbf{William Pensec}, Francesco Regazzoni, Vianney Lapôtre, and Guy Gogniat. Defending the Citadel: Fault Injection Attacks Against Dynamic Information Flow Tracking and Related Countermeasures. 2024 IEEE Computer Society Annual Symposium on VLSI (ISVLSI), 2024, pp. 180-185.~\cite{PRLG-24-isvlsi}}
            \item {\footnotesize\textbf{William Pensec}, Vianney Lapôtre, and Guy Gogniat. Scripting the Unpredictable: Automate Fault Injection in RTL Simulation for Vulnerability Assessment. 2024 27th Euromicro Conference on Digital System Design (DSD), 2024.~\cite{PLG-24-dsd}}
        \end{enumerate}
    \end{block}

    \begin{block}{Source code}
        \begin{itemize}
            \item {\footnotesize \textbf{William Pensec}, FISSA: Fault Injection Simulation for Security Assessment, \url{https://github.com/WilliamPsc/FISSA}}
        \end{itemize}
    \end{block}

    \begin{block}{Popularising science event}
        \begin{itemize}
            \item {\footnotesize Participation in a science outreach event, “\textit{Ma thèse en 180 secondes}” (“My thesis in 180 seconds”), Rennes, March 2023, \url{https://youtu.be/m_whL8xGbMQ}}
        \end{itemize}
    \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
    \backpage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%